HO unification from object language to meta language

### 2024-02-26 paper/main.tex
update tex

@@

\noindent
- how we transform an fo\_tm in tm \\
- the role of links \\
- decomp
- esempio che va in questa semplice rappresentazione (from intro)
- esempio che non va, multi-var, eta, beta
% \section{Term de-compilation}

\section{Unification in ML}

- we accept HO unif with PF \\
- need of multiple vars for a single OL var

% Compile FO to HO

% Assignement in HO should be decompiled

% -------------------------------------------------------------------

% \noindent

>>>>

\otext{Goal: $s_1 \Uo s_2$ is compiled into $t_1 \Ue t_2$}
\otext{What is done: uvars \elpiIn{fo_uv} of OL are replaced into uvars \elpiIn{ho_uv} of the ML}
\otext{Each \elpiIn{fo_uv} is linked to an \elpiIn{ho_uv} of the OL}
\otext{Example: \elpiIn{lam x\ app[uv 0, x] ~\Ue~lam x\ c"f"}}
\otext{Links used to instantiate vars of elpi}
\otext{After all links, the solution in links are compacted and given to coq}
\otext{It is not so simple, see next sections (multi-vars, eta, beta)}

@@

\section{Use of multivars}

\subsection{Problems with $\eta$}
\otext{The following goal: \elpiIn{X = lam x\ lam y\ Y x y, X = lam x\ f}}
\otext{The snd unif pb, we have to unif \elpiIn{lam x\ lam y\ Y x y} with \elpiIn{lam x\ f}}
\otext{It is not doable, with the same elpi var}

\subsection{Problems with $\beta$}

\otext{The following goal: \elpiIn{X = lam x\ x, app[X, 3] = 3}}
\otext{We use links-beta}

\section{First order approximation}

\otext{Coq can solve this: \coqIn{f 1 2 = X 2}, by setting X to f 1}
\otext{We can re-use part of the algo for $\beta$ given before}

\section{Unif encoding in real life}
\otext{Il ML presentato qui è esattamente elpi}
\otext{Il OL presentato qui è esattamente coq}
\otext{Come implementatiamo tutto ciò nel solver}

\section{Results: stdpp and tlc}
\otext{How may rule are we solving?}
\otext{Can we do some perf test}

\section{Conclusion}
